### 2021-02-26 yfcc100m/paper/vldb2021/appendix-eval-plots.tex

Figure~\ref{fig:q_throughput_16} shows the measured throughput,
as images per second, delivered by each system for all queries and databases.
In comparison to figure~\ref{fig:q_throughput_56}, when using fewer concurrent 
clients (nthr = 16), the throughput for VDMS for queries \textit{q4} (\textit{2tag\_or\_resize}), 
\textit{q5} (\textit{2tag\_resize\_geo\_and}), and
\textit{q6} (\textit{2tag\_resize\_geo\_or}) improved by a large margin 
for the 50M and 100M databases. 
In the case of \textit{q4} and \textit{q6}, the throughput for 50M (and 100M for \textit{q4})
increase by a large margin which outperforms both baselines while in figure~\ref{fig:q_throughput_56}
PostgreSQL slightly performed better than VDMS. 
In the case of \textit{q5}, all systems perform a little differently for databases
larger than 5M.  The gaps between the throughput of each system narrows at 10M.  
At a database size of 50M, the performance of the baselines drastically drop
while the throughput of VDMS has a large improvement in comparison.

@@

Figure~\ref{fig:summary_mysql} summarizes the results
comparing VDMS and MySQL. We see up to 96x speedup (for the case of \textit{q2}),
and an average improvement in throughput of about 31x.
We also see how \textit{q3} and \textit{q5} have poor performances and scalability
as the database size grows same as shown in Figure~\ref{fig:summary_postgresql}.
Considering all other queries (\textit{q1}, \textit{q2}, \textit{q4}, and \textit{q6}), 
VDMS provides at least 3x speedup in throughput.

>>>>

Figure~\ref{fig:q_throughput_16} shows the measured throughput,
as images per second, delivered by each system for all queries and databases.
In comparison to figure~\ref{fig:q_throughput_56}, when using fewer concurrent 
clients (nthr = 16), the throughput for VDMS for queries \textit{q4} (\textit{2tag\_or\_resize}), 
\textit{q5} (\textit{2tag\_resize\_geo\_and}), and
\textit{q6} (\textit{2tag\_resize\_geo\_or}) improved by a large margin 
for the 50M and 100M databases. 
In the case of \textit{q4} and \textit{q6}, the throughput for 50M (and 100M for \textit{q4})
increase by a large margin which outperforms both baselines while, in figure~\ref{fig:q_throughput_56},
PostgreSQL slightly performed better than VDMS. 
In the case of \textit{q5}, all systems perform a little differently for databases
larger than 5M.  The gaps between the throughput of each system narrows at 10M.  
At a database size of 50M, the performance of the baselines drastically drop
while the throughput of VDMS has a large improvement in comparison.

@@

Figure~\ref{fig:summary_mysql} summarizes the results
comparing VDMS and MySQL. We see up to 96x speedup (for the case of \textit{q2}),
and an average improvement in throughput of about 31x.
We also see how \textit{q3} and \textit{q5} have poor performances and scalability
as the database size grows, same as shown in Figure~\ref{fig:summary_postgresql}.
Considering all other queries (\textit{q1}, \textit{q2}, \textit{q4}, and \textit{q6}), 
VDMS provides at least 3x speedup in throughput.

### 2021-02-26 yfcc100m/paper/vldb2021/eval.tex

\textbf{VDMS:}
For each database size, we created an instance of VDMS using the image/video metadata,
the machine-generated \textit{autotags} associated with
each image/video identifier, and the list of 1,570 \textit{autotags}.
Internally, that information is represented as a property graph,
where we have one node for each image, one node for each tag
(always 1,570 tags), and a connection between each image and its respective tag(s).
For instance, if an image has four \textit{autotags} assigned,
there will be four connections between that image and
the different nodes for those \textit{autotags}.
The probability the \textit{autotag} is present in an image
is expressed as a property in the \textit{connection} between the two nodes.
Figure~\ref{fig:graph_representation} shows an example on two images,
two \textit{autotags}, and the \textit{connections} between
those \textit{autotags} and the images.
Image id 23143252 has two \textit{autotags} assigned:
\textit{Alligator} with probability 0.285, and \textit{Lake} with probability 0.872.
Image id 86756231, on the other hand, has a single \textit{autotags} assigned:
\textit{Alligator} with probability 0.894.
On average there are 8 tags assigned to each image so
there will be around 8 times more connections than images, as shown
in Table~\ref{table:vdmsnodes}.
Also, each image node will contain multiple properties associated
with it (some of which are listed in Section \ref{dataset}).
% Using the Python Client Module, we insert 1,570 nodes for the \textit{autotags},
% and then insert nodes for the YFCC media objects (images or videos)
% with the associated metadata (as properties of the image/video).
% Then, for each image, we add a \textit{connection} between the image node
% and the \textit{autotag} node. The probability of that \textit{autotag}
% being present in that image is stored as a property in that \textit{connection}.
The number of nodes (representing images and \textit{autotags})
are dependent on the database size and the \textit{connections} are responsible for
90\% of the elements in each database instance,
as shown in Table~\ref{table:vdmsnodes}.
It is also important to note that we create indexes for the image identifier,
\textit{autotags} properties, and longitude/latitude coordinates
to enable faster retrieval.

@@

In an attempt to have the best MySQL configuration possible for this use case,
we explore several parameters to increase the performance
of both loading the data, as well as executing the queries.
In particular, MySQL optimizes threads and transactions out-of-box,
but it cannot handle the entire YFCC100M dataset without configuring
specific parameters.
When creating large databases, a data lock may occur to protect the
data from concurrent updates~\cite{mysql_blog}.
To avoid this mechanism, we increased the buffer pool size to
increase the amount of memory allocated to internal data structures.
It is recommended to set the buffer pool size to 60-80\% of the physical
memory size ~\cite{mysql,mysql_blog}.
However, the time to build a database increased.
We later changed  the buffer pool size to a multiple of the default value, i.e. 16x,
which produced the best results for loading time.

@@

\textbf{PostgreSQL-Based System:}
Each PostgreSQL database is created in the exact same manner as MySQL
where data is represented as three tables:
\textit{images}, \textit{taglist}, and \textit{taglist}.
PostgreSQL works well out-of-box and optimizations were not necessary,
as in MySQL, to load or execute queries.
When executing queries for larger databases,
it is pertinent to have enough disk space for both
the database and tablespace.
The tablespace is associated with a database and stores the temporary files
created within the database object ~\cite{postgresql}.
When processing the larger databases, additional
storage may be needed for the tablespace or a diskfull error may occur.
To avoid this, we allocated a separate SSD disk specifically
for the tablespace of all databases.

@@

In the case of VDMS, we did not attempt to tune any
parameter to avoid unfairness in the comparison against the baselines.
Unlike the baselines, VDMS can handle the entire YFCC100m dataset
using the default parameters provided by the implementation.
For all systems, we created indexes over the
properties we used for search, such as name of
\textit{autotag}, and geo-location values.
Building indexes for the right properties and objects
is basic operation that would be present in any real-world deployment,
and measuring performance without them would lead to useless analysis in our
real-world applications and use cases.

@@

% \subsubsection{Database Building Time}

% One of the first things we noticed is the difference in the time needed to
% build each database, where VDMS outperforms MySQL by a large margin
% but PostgreSQL outperforms VDMS by a large margin as well.
% This analysis includes only the metadata, as the images are stored
% in a shared filesystem. Figure~\ref{fig:db_time_size} illustrates the
% comparison in time to build the databases, and how the speedup
% is sustained as the database size grows.
% Key difference in the build times are attributed to the low-level
% implementation of how MySQL reads and stores data from the files, the
% optimizations (increased InnoDB pool size, etc.) needed
% to handle large datasets such as YFCC100M, and the efficiency of PMGD.
% PostgreSQL Python API can efficiently copy data from files to the database
% which provides an advantage over VDMS which must insert
% multiple nodes/connections per image.
% On average, it took MySQL around $\sim$4x longer to build each database than VDMS,
% and PostgreSQL was around $\sim$21x faster than VDMS.

@@

% Another important aspect to note is the storage footprint of the databases.
PostgreSQL and VDMS require comparable amount of storage for metadata which
is more than required by MySQL, shown in Figure~\ref{fig:db_sizes}.
In the case of VDMS, this is space used to store information about
each node/connection.
The Graph Database internal to VDMS (called PMGD) was designed for performance,
especially in environments where persistent memory is present.
This design decision comes as a trade-off for storage footprint, which is
noticeable in our results.
VDMS required 37-41\% more storage than MySQL for storing the same amount
of metadata. On the other hand, PostgreSQL required 1-4\% more storage than VDMS.
The storage footprint may become a factor if storage is a limitation, but
it should also be noted that metadata accounts for less than 2\% of the
overall database size even if we have a 41\% increase in metadata size.
For example, the largest database (both metadata and images) we built
(100M) has around 230GB of metadata and 12TB of images.
In systems where persistent memory is a scarce resource,
the increased storage footprint of PMGD may represent a challenge.
On the other hand, persistent memory is expected to be available
in the order of TBs per server, which should fit the
metadata of intensive use-cases\cite{IntelXPoint15}.

>>>>

\textbf{VDMS:}
For each database size, we created an instance of VDMS using the image/video metadata,
the machine-generated \textit{autotags} associated with
each image/video identifier, and the list of 1,570 \textit{autotags}.
Internally, that information is represented as a graph,
where we have one node for each image, one node for each tag
(always 1,570 tags), and a connection between each image and its respective tag(s).
For instance, if an image has four \textit{autotags} assigned,
there will be four connections between that image and
the different nodes for those \textit{autotags}.
The probability the \textit{autotag} is present in an image
is expressed as a property in the \textit{connection} between the two nodes.
Figure~\ref{fig:graph_representation} shows an example on two images,
two \textit{autotags}, and the \textit{connections} between
those \textit{autotags} and the images.
Image id 23143252 has two \textit{autotags} assigned:
\textit{Alligator} with probability 0.285, and \textit{Lake} with probability 0.872.
Image id 86756231, on the other hand, has a single \textit{autotags} assigned:
\textit{Alligator} with probability 0.894.
On average there are 8 tags assigned to each image so
there will be around 8 times more connections than images, as shown
in Table~\ref{table:vdmsnodes}.
Also, each image node will contain multiple properties associated
with it (some of which are listed in Section \ref{dataset}).
% Using the Python Client Module, we insert 1,570 nodes for the \textit{autotags},
% and then insert nodes for the YFCC media objects (images or videos)
% with the associated metadata (as properties of the image/video).
% Then, for each image, we add a \textit{connection} between the image node
% and the \textit{autotag} node. The probability of that \textit{autotag}
% being present in that image is stored as a property in that \textit{connection}.
The number of nodes (representing images and \textit{autotags})
are dependent on the database size and the \textit{connections} are responsible for
90\% of the elements in each database instance,
as shown in Table~\ref{table:vdmsnodes}.
It is also important to note that we create indexes for the image identifier,
\textit{autotags} properties, and longitude/latitude coordinates
to enable faster retrieval.

@@

In an attempt to have the best MySQL configuration possible for this use case,
we explore several parameters to increase the performance
of both loading the data, as well as executing the queries.
In particular, MySQL optimizes threads and transactions out-of-box,
but it cannot handle the entire YFCC100M dataset without configuring
specific parameters.
When creating large databases, a data lock may occur to protect the
data from concurrent updates~\cite{mysql_blog}.
To avoid this mechanism, we increased the buffer pool size to
increase the amount of memory allocated to internal data structures.
It is recommended to set the buffer pool size to 60-80\% of the physical
memory size ~\cite{mysql,mysql_blog}.
However, the time to build a database increased.
We later changed  the buffer pool size to be 16x the default value,
where we saw the best performance.

@@

\textbf{PostgreSQL-Based System:}
Each PostgreSQL database is created in the exact same manner as MySQL
where data is represented as three tables:
\textit{images}, \textit{taglist}, and \textit{taglist}.
PostgreSQL works well out-of-box and optimizations were not necessary,
as in MySQL, to load or execute queries.
When executing queries for larger databases,
it is pertinent to have enough disk space for both
the database and tablespace.
The tablespace is associated with a database and stores the temporary files
created within the database object ~\cite{postgresql}.
When processing the larger databases, additional
storage may be needed for the tablespace or a diskfull error may occur.
To avoid this, we allocated a separate SSD disk specifically
for the tablespace of all databases.
This was required, specially for 100M database, in order to make the queries
complete execution without failures, and represented a big disadvantage
in terms of the disk space footprint during query execution.

@@

In the case of VDMS, we did not attempt to tune any
parameter to avoid unfairness in the comparison against the baselines.
Unlike the baselines, VDMS can handle the entire YFCC100m dataset
using the default parameters provided by the implementation.

\subsubsection{Indexes:}
For all systems, we created indexes over the
properties we used for search, such as name of
\textit{autotag}, and geo-location values.
Building indexes for the right properties and objects
is basic operation that would be present in any real-world deployment,
and measuring performance without them would lead to useless analysis in our
real-world applications and use cases.

@@

@@

The Graph Database used by VDMS (PMGD) was designed for performance,
especially in environments where persistent memory is present.
This design decision comes as a trade-off for storage footprint, which is
noticeable in other PMGD evaluation we have run in the past.
Because PMGD was not optimized for low storage footprint, authors feared that
any improvement would come at the expenses of a significant increase on
disk occupancy.
We measured metadata disk footprint for that reason, and show the results
in Figure~\ref{fig:db_sizes}.
PostgreSQL and VDMS require comparable amount of storage for metadata which
is more than required by MySQL, shown in Figure~\ref{fig:db_sizes}.
In the case of VDMS, this is space used to store information about
each node/connection.
VDMS required 37-41\% more storage than MySQL for storing the same amount
of metadata. On the other hand, PostgreSQL required 1-4\% more storage than VDMS.
The storage footprint may become a factor if storage is a limitation, but
it should also be noted that metadata accounts for less than 2\% of the
overall database size even if we have a 41\% increase in metadata size.
For example, the largest database (both metadata and images) we built
(100M) has around 230GB of metadata and 12TB of images.
In systems where persistent memory is a scarce resource,
the increased storage footprint of PMGD may represent a challenge.
On the other hand, persistent memory is expected to be available
in the order of TBs per server, which should fit the
metadata of intensive use-cases\cite{IntelXPoint15}.
